---
title: "How Do Users Review Spotify?"
subtitle: "Analyzing Emotion, Topics, and Platform Replies Using TAD and Logistic Regression"
authors:
  - name: Yihan Chen
    email: yc1140@georgetown.edu
    affiliation: Georgetown University
    corresponding: true
df-print: kable
title-block-banner: "figures/spotify_cover.png" 
title-block-banner-color: black  
format:
  html:
    toc: true
    toc-depth: 3
    df-print: kable
    code-fold: true
    code-tools: true
    code-summary: "Show Code"
editor:
  markdown:
    wrap: 72
---

## 1. Introduction

```{r setup, include=FALSE}
pacman::p_load(openxlsx, readxl, tidyverse, tidytext, textclean, hunspell, quanteda, quanteda.textplots, quanteda.textstats,
               quanteda.textmodels, rjson, janitor, stm, topicmodels, broom.mixed, caret, naivebayes,
               glmnet, e1071, ggplot2, purrr, textmineR, wordcloud, RColorBrewer, pscl, gridExtra, patchwork, scales, modelsummary, smotefamily)
rm(list=ls())
```

### 1.1 Background

Spotify has become the global leader in music streaming, with over 252
million premium subscribers as of Q3 2024 [(Statista,
2024)](https://www.statista.com/statistics/244995/number-of-paying-spotify-subscribers/).

While subscription metrics reveal growth, understanding user
satisfaction and retention requires deeper analysis beyond numerical
figures. User-generated content (UGC), especially app store reviews,
provides rich insights into customer experiences. These reviews reflect
not only product satisfaction but also user frustrations and unmet
expectations. Platforms like Spotify occasionally respond to user
reviews, but the dynamics of which reviews receive replies remain
largely unexplored.

From a **business strategy** perspective, responding to user feedback
can enhance loyalty, mitigate churn risks, and signal active customer
engagement. From a **policy** perspective, increasing attention is being
paid to platform transparency, consumer protection, and fairness in
digital services [(OECD,
2022)](https://www.oecd.org/digital/consumer-protection/).

Understanding how Spotify engages with user feedback through public
responses has important implications for platform governance, user
retention strategies, and broader digital platform accountability.

```{r spotify-premium-subscribers, echo=FALSE, warning=FALSE, message=FALSE}
spotify_data <- data.frame(
  quarter = c("Q1 2015", "Q3 2015", "Q1 2016", "Q3 2016", "Q1 2017", "Q3 2017",
              "Q1 2018", "Q3 2018", "Q1 2019", "Q3 2019", "Q1 2020", "Q3 2020",
              "Q1 2021", "Q3 2021", "Q1 2022", "Q3 2022", "Q1 2023", "Q3 2023", 
              "Q1 2024", "Q3 2024"),
  subscribers_million = c(18, 22, 28, 30, 48, 52, 71, 75, 96, 100, 124, 130, 
                           155, 165, 182, 195, 226, 239, 246, 252)
)

spotify_data$quarter <- factor(spotify_data$quarter, levels = spotify_data$quarter)

ggplot(spotify_data, aes(x = quarter, y = subscribers_million, group = 1)) +
  geom_col(fill = "#78C2AD") +  
  geom_line(color = "#2C6E49", size = 1.2) +  
  geom_point(color = "#2C6E49", size = 2) +   
  labs(
    title = "Growth of Spotify Premium Subscribers (2015–2024)",
    subtitle = "Spotify surpassed 252 million premium subscribers as of Q3 2024",
    x = "Quarter",
    y = "Subscribers (Millions)",
    caption = "Source: Statista (2024)"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold"),
    plot.subtitle = element_text(color = "gray30"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.minor = element_blank()
  )
```

------------------------------------------------------------------------

### 1.2 Literature Review

Literature supports that text analysis informs consumer insights. [Pang
& Lee (2008)](https://www.nowpublishers.com/article/Details/INR-011),
[Liu (2012)](https://link.springer.com/book/10.1007/978-3-031-02145-9)
made the foundation of sentiment analysis for understanding customer
satisfaction. [Tirunillai & Tellis
(2012)](https://www.researchgate.net/publication/228151131_Does_Online_Chatter_Really_Matter_Dynamics_of_User-Generated_Content_and_Stock_Performance)
showed that user-generated content predicts business performance, while
[Blei et al.
(2003)](https://www.researchgate.net/publication/221620547_Latent_Dirichlet_Allocation)
introduced LDA topic modeling to identify consumer concerns. In digital
media, [Datta et al.
(2018)](https://www.researchgate.net/publication/293753759_Changing_Their_Tune_How_Consumers%27_Adoption_of_Online_Streaming_Affects_Music_Consumption_and_Discovery)
found that users' sentiments correlate with music subscriber growth, and
[Piskorski et al.
(2019)](https://www.researchgate.net/publication/275947382_Social_Media_and_Customer_Retention_Implications_for_the_Luxury_Beauty_Industry)
demonstrated that negative sentiment spikes signal churn risk. These
findings help to support the analysis of user sentiment in Spotify's
reviews and help to make market decisions.

------------------------------------------------------------------------

### 1.3 Research Questions & Hypotheses

This project is guided by the following research questions and
associated hypotheses:

-   **RQ1**: How do Spotify users describe their experience in written
    reviews?

    **H1**: A majority of user reviews focus on app functionality,
    usability, and technical performance rather than music content.

-   **RQ2**: Which review topics or tones are more likely to receive an
    official reply---and what does this reveal about platform priorities
    or transparency?

    **H2**: Reviews expressing dissatisfaction, especially those
    highlighting technical issues or account problems, are more likely
    to receive a reply than general positive feedback.

------------------------------------------------------------------------

### 1.4 Methodology Overview

This project combines **manual annotation**, **supervised machine
learning**, **unsupervised topic modeling**, **sentiment analysis**, and
**logistic regression** to investigate the content and platform
engagement patterns of over 61,000 Spotify app user reviews. The primary
goal is to classify user feedback into categories and evaluate how
different review characteristics correlate with the likelihood of
receiving an official platform reply.

The analysis is structured in three major phases:

1.  **Classification of User Reviews**\
    A subset (\~2000) of reviews was manually annotated into *App
    Experience* (e.g., technical issues, UX features) and *Other*
    categories (e.g., music content, ad & pricing, public opinion on
    Spotify company, general feedback). Using this labeled set, I
    trained multiple text classification models (Naïve Bayes, SVM,
    Lasso) based on TF-IDF features. I also tested if word embedding
    using pre-trained GloVe vectors would improve the Lasso model. The
    final model---**Lasso with TF-IDF**---was selected for its high
    accuracy (83%) and interpretability. This model was applied to
    classify all reviews in the dataset.

2.  **Topic Modeling on App Experience**\
    To explore subthemes within *App Experience* reviews, I applied
    **Latent Dirichlet Allocation (LDA)**. Six distinct topics were
    identified, including *Technical Fixes*, *Account & Subscription
    Issues*, *Playback Problems*, and *Positive Feedback*. These topic
    labels were merged back into the main dataset for further analysis.
    The *Other* category for the rest observations was also labeled as
    *Other* for this variable.

3.  **Platform Reply Analysis**\
    Only 0.35% of user reviews received an official reply from Spotify.
    To explore patterns in reply behavior, I:

    -   Conducted **emotion scoring** using the **NRC lexicon**
    -   Constructed logistic regression models to predict replies based
        on emotional tone, review length, topic labels, and competitor
        mentions

This approach allows for both categorization and insights into platform
responsiveness, user frustration, and policy-relevant themes like
fairness, transparency, and user protection.

## 🔧 Data Wrangling Steps

To prepare the dataset for analysis, I implemented the following structured data cleaning and transformation pipeline:

- **Text Cleaning:** Converted all review text to lowercase, removed duplicates, and eliminated special characters to ensure consistency for text-based analysis.
- **Tokenization & Lexicon Matching:** Tokenized review text and joined with the NRC lexicon to generate review-level emotion scores across ten emotion categories.
- **Manual Annotation:** Labeled a 2,000-review sample into high-level categories (e.g., App Experience vs. Other) to enable supervised learning.
- **Feature Engineering:**
  - Created binary flags for official reply status and competitor mentions (e.g., detecting "apple music").
  - Computed review-level features including word count and presence of competitor names using regex patterns.
- **Text Classification:** Built TF-IDF and word embedding matrices to classify reviews into predicted topic labels using machine learning models.
- **Topic Modeling Preparation:** Filtered and pre-processed App Experience reviews for use in unsupervised LDA modeling.
- **SMOTE Balancing:** Addressed reply class imbalance by generating synthetic samples for the minority class (Replied = 1) to support robust logistic regression modeling.
- **Reshaping for Visualization:** Transformed wide-format data (emotion scores, topic labels, etc.) into long-format using `pivot_longer` to enable flexible plotting and faceted visualizations.


### 1.5 Variable of Interest

The full dataset (*newreview*) includes the following variables:

- Review: The review text

- Rating: Star rating (1 to 5)

- Predicted_Label: Binary classification output (App Experience vs. Other)

- Sentiment: Derived from star rating (Negative, Neutral, Positive)

- Replied: Binary indicator for whether Spotify replied

- PredictedLabel_LDA: Topic label from LDA modeling

- Emotion Scores (from NRC Lexicon): anticipation, joy, positive, sadness, trust, anger, fear, negative, surprise, disgust

- word_count: Total number of words in the review

- competitor_mention: Binary indicator for whether a competing platform was mentioned
------------------------------------------------------------------------

## 2. Data & Annotation

### 2.1 Data Loading and Cleaning

The primary dataset used in this analysis consists of **61,594 user
reviews** of the Spotify mobile application, scraped from the **Google
Play Store** and published on [Kaggle
(2022)](https://www.kaggle.com/datasets/mfaaris/spotify-app-reviews-2022).
Each observation includes:

-   `Time_submitted`: the timestamp of when the review was posted,\
-   `Review`: the full text of the user's review,\
-   `Rating`: a numeric star rating from 1 (lowest) to 5 (highest),\
-   `Total_thumbsup`: the number of other users who marked the review as
    helpful,\
-   `Reply`: the official response from Spotify, if any.

Initial inspection confirmed the dataset is clean and complete, with
**no missing values** in any of the five key fields. Reviews were
filtered to remove empty entries and were subsequently preprocessed to
standardize formatting. Preprocessing steps included expanding
contractions (e.g., "isn't" → "is not"), removing special characters,
converting numbers to words, and ensuring consistent encoding. This
prepared the data for downstream natural language processing tasks such
as classification and sentiment analysis.

```{r load-review-data, eval=FALSE}
review <- read.csv("data/reviews.csv")
review <- review %>%
  mutate(Review = Review %>%
           replace_contraction() %>%
           replace_word_elongation() %>%
           replace_symbol() %>%
           replace_number() %>%
           replace_non_ascii()) %>%
  drop_na(Review) %>%
  filter(Review != "")

write.csv(review, "data/processed_reviews.csv", row.names = FALSE)
```

```{r load-review-data-quick, message=FALSE, warning=FALSE}
review <- read.csv("data/processed_reviews.csv")
```

```{r for duplicate, include=FALSE}
review %>%
  group_by(Review) %>%
  filter(n() > 1) %>%
  arrange(Review) %>%
  slice_head(n = 5) %>%
  print(n = 5)
```

------------------------------------------------------------------------

### 2.2 Human Annotation

Using a manually labeled random sample of 2,000 reviews, I initially
created four function-based categories according to the major themes
mentioned in reviews:

-   **Technical Issues**: problems with the functionality or stability
    of the app.
-   **UX and Features**: user experience, layout, and feature-related
    feedback.
-   **Price and Ads**: complaints about subscriptions, pricing, or ad
    interruptions.
-   **Other**: general impressions or unrelated comments.

However, due to the overlapping nature of many reviews and difficulty
distinguishing between certain categories (e.g., Technical vs.
UX_Feature), I consolidated these labels into a binary classification
scheme to improve annotation consistency and model performance:

-   **App Experience**: includes reviews related to technical issues,
    user interface, and features ("Technical Issues" plus "UX and
    Features").
-   **Other**: includes vague or general sentiment not tied to specific
    app functionalities ("Price and Ads" and "Other").

This consolidation allows the classifier to focus on identifying whether
a review pertains to actionable app experience issues. Reviews
referencing music content (e.g., "variety of songs") or expressing
general satisfaction were generally categorized under *Other* unless
they contained explicit comments about app use.

```{r label-data, message=FALSE, warning=FALSE}
checked <- read_excel("data/human_label_checked.xlsx")
checked$NewLabel[checked$NewLabel %in% c("Technical", "UX_Feature")] <- "App Experience"
checked$NewLabel[!checked$NewLabel %in% c("App Experience")] <- "Other"
checked$NewLabel <- factor(checked$NewLabel)
```

------------------------------------------------------------------------

## 3. Classification

### 3.1 TF-IDF Feature Matrix and Split

To prepare the dataset for supervised machine learning models, I
initially considered manually constructing three distinct subsets,
including a validation set, to enable separate evaluation across
multiple methods. While this approach would have ensured independent
validation for each model, it would have significantly reduced the
available training data, potentially weakening model performance due to
limited sample size.

Recognizing this trade-off, I adopted an alternative strategy to
maximize data utilization. Specifically, I performed a random 80:20
split of the full labeled dataset into training and test sets. To
further improve model robustness and generalizability, cross-validation
techniques were applied within the training set during model tuning:

-   **Naïve Bayes**: Evaluated using 5-fold cross-validation.

-   **Support Vector Machine (SVM)**: Hyperparameter tuning via
    cross-validation.

-   **Lasso (Logistic Regression with L1 Penalty)**: Utilized built-in
    cross-validation available through the cv.glmnet() function.

Following the split, text preprocessing was conducted separately for the
training and test sets. Tokenization was applied with the removal of
punctuation, numbers, and symbols, followed by stemming and stopword
removal. A term-frequency inverse-document-frequency (TF-IDF) weighting
scheme was then used to construct the feature matrices, ensuring that
both sets were aligned on the same vocabulary.

```{r tfidf-split, message=FALSE, warning=FALSE}
train_index <- createDataPartition(checked$ID, p = 0.8, list = FALSE)
trainSet <- checked[train_index, ]
testSet <- checked[-train_index, ]

train_dfm <- tokens(trainSet$Review, remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
  dfm() %>%
  dfm_wordstem() %>%
  dfm_remove(stopwords("en")) %>%
  dfm_trim(min_docfreq = 0.001, max_docfreq = 0.999, docfreq_type = "prop")

test_dfm <- tokens(testSet$Review, remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
  dfm() %>%
  dfm_wordstem() %>%
  dfm_remove(stopwords("en")) %>%
  dfm_match(features = featnames(train_dfm))

train_tfidf <- dfm_tfidf(train_dfm)
test_tfidf <- dfm_tfidf(test_dfm)

train_matrix <- as.matrix(train_tfidf)
test_matrix  <- as.matrix(test_tfidf)

testSet$NewLabel <- factor(testSet$NewLabel, levels = c("App Experience", "Other"))
```

------------------------------------------------------------------------

### 3.2 Supervised Machine Learning

After constructing the TF-IDF feature matrices, three supervised machine
learning models were trained to classify Spotify user reviews: Naïve
Bayes, SVM, and Lasso. For reproducibility and potential future
applications, all trained models and associated feature sets were saved
to disk. Detailed modeling procedures and results are described below.

#### 3.2.1 Naïve Bayes with Cross-Validation

The Naïve Bayes classifier was initially evaluated using both raw
document-feature matrices (DFM) and TF-IDF weighted matrices. Empirical
testing showed that the TF-IDF transformation consistently improved
model performance, and thus it was adopted for all modeling.

A 5-fold cross-validation strategy was employed to estimate model
performance during training. In each fold, the training set was further
split into a smaller training subset and a validation subset, and model
accuracy was recorded. The final model was then retrained on the full
training set and evaluated on the held-out test set.

```{r nb-tfidf-model, eval=FALSE}
set.seed(2025323)
folds <- createFolds(trainSet$NewLabel, k = 5, list = TRUE)
docnames(train_tfidf) <- trainSet$ID

cv_results <- lapply(folds, function(test_indices) {
  validation_cv <- trainSet[test_indices, ]
  train_cv <- trainSet[-test_indices, ]

  train_cv_dfm <- dfm_subset(train_tfidf, docnames(train_tfidf) %in% train_cv$ID)
  validation_cv_dfm <- dfm_subset(train_tfidf, docnames(train_tfidf) %in% validation_cv$ID)
  validation_cv_dfm <- dfm_match(validation_cv_dfm, features = featnames(train_cv_dfm))

  nb_model_cv <- textmodel_nb(train_cv_dfm, train_cv$NewLabel, smooth = 1, prior = "docfreq")
  predicted_cv <- predict(nb_model_cv, newdata = validation_cv_dfm)
  predicted_cv <- factor(predicted_cv, levels = c("App Experience", "Other"))
  validation_cv$NewLabel <- factor(validation_cv$NewLabel, levels = c("App Experience", "Other"))

  if (length(unique(validation_cv$NewLabel)) < 2) return(NA)
  cv_cmat <- confusionMatrix(table(predicted_cv, validation_cv$NewLabel))
  return(cv_cmat$overall["Accuracy"])
})

cv_results <- na.omit(unlist(cv_results))
mean_cv_accuracy <- mean(cv_results, na.rm = TRUE)
cat("Mean 5-Fold CV Accuracy:", round(mean_cv_accuracy, 3), "\n")

nb_model <- textmodel_nb(train_tfidf, trainSet$NewLabel, smooth = 1, prior = "docfreq")
saveRDS(nb_model, "model/nb_model.rds")
predicted_test_nb <- predict(nb_model, newdata = test_tfidf)
predicted_test_nb <- factor(predicted_test_nb, levels = c("App Experience", "Other"))
test_cmat_nb <- confusionMatrix(predicted_test_nb, testSet$NewLabel)
print(test_cmat_nb)
```

------------------------------------------------------------------------

#### 3.2.2 SVM Model

A linear kernel SVM model was trained on the TF-IDF matrix. To optimize
model performance, hyperparameter tuning was performed on the cost
parameter (C) using 5-fold cross-validation. Although minor scaling
warnings were encountered due to sparsity in the TF-IDF matrix, careful
feature trimming was conducted to minimize these issues without
significantly altering the vocabulary set.

```{r svm-tfidf-model, eval=FALSE}
set.seed(2025323)
svm_tuned <- tune(
  svm,
  train.x = train_matrix,
  train.y = as.factor(trainSet$NewLabel),
  kernel = "linear",
  ranges = list(cost = c(0.1, 1, 10)),
  tunecontrol = tune.control(cross = 5)
)

svm_model <- svm_tuned$best.model
predicted_test_svm <- predict(svm_model, newdata = test_matrix)
predicted_test_svm <- factor(predicted_test_svm, levels = c("App Experience", "Other"))
test_cmat_svm <- confusionMatrix(predicted_test_svm, testSet$NewLabel)
print(test_cmat_svm)
saveRDS(svm_model, "model/svm_model.rds")
```

------------------------------------------------------------------------

#### 3.2.3 Lasso Model

A Lasso logistic regression model was fitted to the TF-IDF matrix using
cv.glmnet(), which automatically performs internal cross-validation to
select the optimal regularization parameter (lambda). A binomial family
was specified to handle the binary classification task.

```{r lasso-tfidf-model, eval=FALSE}
set.seed(2025323)
lasso_model <- cv.glmnet(
  x = as.matrix(train_tfidf),
  y = trainSet$NewLabel,
  family = "binomial",
  alpha = 1,
  nfolds = 5,
  type.measure = "class",
  lambda.min.ratio = 1e-3,
  maxit = 50000
)

plot(lasso_model)
print(lasso_model)

predicted_test_lasso <- predict(lasso_model, newx = test_matrix, s = "lambda.min", type = "class")
predicted_test_lasso <- factor(predicted_test_lasso, levels = c("App Experience", "Other"))
test_cmat_lasso <- confusionMatrix(predicted_test_lasso, testSet$NewLabel)
print(test_cmat_lasso)
saveRDS(lasso_model, "model/lasso_model.rds")
```

------------------------------------------------------------------------

#### 3.2.4 Comparison of Models

To ensure consistency and efficiency, the trained models were saved and
reloaded for performance comparison without needing to re-run the full
training pipelines. The saved models were applied to the held-out test
set, ensuring that feature alignment was maintained between training and
testing phases.

```{r compare-models-tfidf, eval=FALSE}
cat("Naïve Bayes Test Set Accuracy:", round(test_cmat_nb$overall["Accuracy"], 3), "\n")
cat("SVM Test Accuracy:", round(test_cmat_svm$overall["Accuracy"], 3), "\n")
cat("Lasso Test Set Accuracy:", round(test_cmat_lasso$overall["Accuracy"], 3), "\n")
```

Based on previously recorded results:

-   **Naïve Bayes Test Set Accuracy**: 0.785
-   **SVM Test Set Accuracy**: 0.785
-   **Lasso Test Set Accuracy**: 0.83

Lasso outperformed the other two models and demonstrated the highest
accuracy in classifying Spotify reviews into *App Experience* and
*Other* categories. It was followed by SVM and Naïve Bayes, which
performed similarly.

------------------------------------------------------------------------

#### 3.2.5 Embedding-based Classification

To further explore performance improvements, an embedding-based
classification approach was implemented. Each review was represented as
the average of its constituent word embeddings, using [pre-trained
300-dimensional GloVe vectors](https://nlp.stanford.edu/projects/glove/). The resulting document
embeddings were then used to train a Lasso logistic regression model.

```{r glove-embedding-classification, eval=FALSE}
# === Load Pretrained Embeddings ===
glove_path <- "data/glove.6B.300d.txt"  # download from https://nlp.stanford.edu/projects/glove/
glove_wts <- data.table::fread(glove_path, quote = "", data.table = FALSE) %>% as_tibble()
glove_matrix <- as.matrix(glove_wts[,-1])
rownames(glove_matrix) <- glove_wts$V1

# === Create Document Embeddings ===
dfm_embed <- tokens(checked$Review,
                   remove_punct = TRUE,
                   remove_numbers = TRUE,
                   remove_symbols = TRUE) %>%
  dfm() %>%
  dfm_remove(stopwords("en"))

w2v <- glove_matrix[rownames(glove_matrix) %in% featnames(dfm_embed), ]

embed <- matrix(NA, nrow = ndoc(dfm_embed), ncol = 300)
for (i in 1:ndoc(dfm_embed)) {
  vec <- as.numeric(dfm_embed[i,])
  doc_words <- featnames(dfm_embed)[vec > 0]
  embed_vec <- w2v[rownames(w2v) %in% doc_words, ]
  embed[i,] <- if (is.null(dim(embed_vec))) rep(NA, 300) else colMeans(embed_vec, na.rm = TRUE)
}

rows_with_na <- apply(embed, 1, function(row) any(is.na(row)))
embed_clean <- embed[!rows_with_na, ]
checked_clean <- checked[!rows_with_na, ]

set.seed(2025323)
train_index <- createDataPartition(checked_clean$NewLabel, p = 0.8, list = FALSE)
X_train_embed <- embed_clean[train_index, ]
X_test_embed  <- embed_clean[-train_index, ]
y_train_embed <- checked_clean$NewLabel[train_index]
y_test_embed  <- checked_clean$NewLabel[-train_index]

# === Train and Save Embedding Lasso Model ===
lasso_embed <- cv.glmnet(X_train_embed, y_train_embed,
                         family = "binomial", alpha = 1,
                         nfolds = 5, maxit = 50000)

preds_embed <- predict(lasso_embed, newx = X_test_embed, s = "lambda.min", type = "class")
preds_embed <- factor(preds_embed, levels = levels(y_test_embed))
confusionMatrix(preds_embed, y_test_embed)

saveRDS(lasso_embed, "model/final_embedding_lasso_model.rds")
```

To systematically compare the TF-IDF-based and embedding-based models,
evaluation metrics including accuracy, precision, recall, F1 score, and
balanced accuracy were computed.

```{r compare 2 lasso, eval=FALSE}
compare_models <- function(model_name, preds, truth) {
  cm <- confusionMatrix(preds, truth)
  acc <- round(cm$overall["Accuracy"], 3)
  kappa <- round(cm$overall["Kappa"], 3)

  precision <- round(cm$byClass["Precision"], 3)
  recall <- round(cm$byClass["Recall"], 3)
  f1 <- round(2 * (precision * recall) / (precision + recall), 3)
  bal_acc <- round(cm$byClass["Balanced Accuracy"], 3)

  cat("==========", model_name, "==========\n")
  cat("Accuracy:", acc, "\n")
  cat("Kappa:", kappa, "\n")
  cat("Precision:", precision, "\n")
  cat("Recall:", recall, "\n")
  cat("F1 Score:", f1, "\n")
  cat("Balanced Accuracy:", bal_acc, "\n\n")
}

compare_models("TF-IDF Lasso", predicted_test_lasso, testSet$NewLabel)
compare_models("Word Embedding Lasso", preds_embed, y_test_embed)
```

Although the embedding-based Lasso model demonstrated strong recall and
comparable F1 performance, the TF-IDF-based Lasso achieved slightly
higher overall accuracy and balanced accuracy. Given its
interpretability and marginally superior performance, the TF-IDF Lasso
was selected as the final classification model.

The following visualization summarizes model comparison results:

```         
========== TF-IDF Lasso ==========
Accuracy: 0.83
Kappa: 0.648
Precision: 0.868
Recall: 0.846
F1 Score: 0.857
Balanced Accuracy: 0.826

========== Word Embedding Lasso ==========
Accuracy: 0.82
Kappa: 0.613
Precision: 0.837
Recall: 0.878
F1 Score: 0.857
Balanced Accuracy: 0.802
```

```{r compare-accuracy, message=FALSE, warning=FALSE}
# Previously recorded accuracy
accuracy_results <- tibble(
  Model = c("Naive Bayes", "SVM", "Lasso (TF-IDF)", "Lasso (Embedding)"),
  Accuracy = c(0.785, 0.785, 0.83, 0.82)
)

ggplot(accuracy_results, aes(x = reorder(Model, Accuracy), y = Accuracy, fill = Model)) +
  geom_col(width = 0.5, show.legend = FALSE) +  # Narrower bars
  geom_text(aes(label = sprintf("%.3f", Accuracy)), vjust = -0.8, size = 4.2, fontface = "bold") +  # Bold and clear labels
  scale_fill_brewer(palette = "Set2") +  # Professional palette
  ylim(0, 1) +
  labs(
    title = "Classification Accuracy Across Models",
    x = NULL,
    y = "Accuracy"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5, size = 14),
    axis.text.x = element_text(size = 11),
    axis.text.y = element_text(size = 10)
  )
```

Given its stronger interpretability and slightly higher overall
performance, TF-IDF Lasso was selected as the primary model for
classifying Spotify reviews.

------------------------------------------------------------------------

#### 3.2.6 Applying Model to Full Dataset

Finally, the selected TF-IDF Lasso model was applied to the entire
cleaned Spotify review dataset to predict categories for all available
reviews.

```{r tfidf-classification-full, eval=FALSE}
# === Preprocess Full Review Set ===
full_dfm <- tokens(review$Review,
                  remove_punct = TRUE,
                  remove_numbers = TRUE,
                  remove_symbols = TRUE) %>%
  dfm() %>%
  dfm_wordstem() %>%
  dfm_remove(stopwords("en")) %>%
  dfm_match(features = featnames(train_tfidf))

full_matrix <- as.matrix(dfm_tfidf(full_dfm))

# === Load Final TF-IDF Model and Predict ===
final_model <- readRDS("model/lasso_model.rds")
predictions_all <- predict(final_model, newx = full_matrix, s = "lambda.min", type = "class")
review$Predicted_Label <- predictions_all
head(review[, c("Review", "Predicted_Label")])

# write.csv(review, "data/predicted_reviews_tfidf_lasso.csv", row.names = FALSE)
```

The resulting predictions provide categorical labels (*App Experience*
or *Other*) for the entire corpus of user reviews, facilitating
downstream sentiment analysis and topic-specific insights.

------------------------------------------------------------------------

## 4. Topic Modeling for App Experience Reviews

### 4.1 Load Predicted Data and Label Sentiment and Reply

Using the star ratings assigned to each review, sentiment labels were
created: 

- 1--2 stars: *Negative* 

- 3 stars: *Neutral* 

- 4--5 stars: *Positive*

Among 60,915 reviews: 

- **40%** were labeled *Negative* 

- **11%** were labeled *Neutral* 

- **49%** were labeled *Positive*

Reply behavior was also examined. Only **0.35%** of reviews received an
official Spotify reply, indicating that responses are extremely rare.

Applying the TF-IDF Lasso classifier: 

- **62%** of reviews were classified as *App Experience* 

- **38%** were classified as *Other*

Most user feedback focused on functionality, usability, or
performance-related aspects of the Spotify app.

```{r load new data, include=FALSE}
# Load predictions from the TF-IDF model
newreview <- read.csv("data/predicted_reviews_tfidf_lasso.csv")

# Label sentiment based on star ratings
newreview$Sentiment <- ifelse(newreview$Rating <= 2, "Negative",
                              ifelse(newreview$Rating == 3, "Neutral", "Positive"))

# Check distribution
# table(newreview$Sentiment)
# prop.table(table(newreview$Sentiment))

# Label whether a review received a reply (1 = Yes, 0 = No)
newreview$Replied <- ifelse(nchar(trimws(newreview$Reply)) > 0, 1, 0)

# Generate count tables
sentiment_table <- table(newreview$Sentiment)
reply_table <- table(newreview$Replied)
label_table <- table(newreview$Predicted_Label)

# Print tables
# sentiment_table
prop.table(sentiment_table)
# reply_table
prop.table(reply_table)
# label_table
prop.table(label_table)
```

```{r plot, message=FALSE, warning=FALSE}
sentiment_dist <- newreview %>% count(Sentiment) %>% mutate(prop = n / sum(n))
reply_dist <- newreview %>% count(Replied) %>% mutate(prop = n / sum(n))
label_dist <- newreview %>% count(Predicted_Label) %>% mutate(prop = n / sum(n))

p1 <- ggplot(sentiment_dist, aes(x = Sentiment, y = prop, fill = Sentiment)) +
  geom_col(show.legend = FALSE) +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "Distribution of Sentiment", y = NULL, x = "Sentiment") +
  scale_fill_brewer(palette = "Set2") +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(size = 12))

p2 <- ggplot(reply_dist, aes(x = factor(Replied), y = prop, fill = factor(Replied))) +
  geom_col(show.legend = FALSE) +
  scale_y_continuous(labels = scales::percent) +
  scale_x_discrete(labels = c("0" = "No Reply", "1" = "Replied")) +
  labs(title = "Reviews with Reply", y = NULL, x = "Reply") +
  scale_fill_brewer(palette = "Set2") +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(size = 12))

p3 <- ggplot(label_dist, aes(x = Predicted_Label, y = prop, fill = Predicted_Label)) +
  geom_col(show.legend = FALSE) +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "Classification Results", y = NULL, x = "Predicted Label") +
  scale_fill_brewer(palette = "Set2") +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(size = 12))

# Combine into one row
p1 + p2 + p3 + plot_layout(ncol = 3)
```

------------------------------------------------------------------------

### 4.2 Duplicate Handling

Upon inspection, 270 duplicated review texts were identified, submitted
by different users. Some identical reviews appeared with different star
ratings, likely reflecting varying individual standards or accidental
misratings.

Rather than removing these duplicates, they were retained to preserve
the richness of user perspectives. This decision captures the subjective
nature of user experiences and provides further insights into rating
inconsistencies across the platform.

```{r check-duplicate-counts, include=FALSE}
sum(duplicated(newreview$Review))
```

```{r check-rating-variation, message=FALSE, warning=FALSE, results = "hide"}
review_variance <- newreview %>%
  group_by(Review) %>%
  summarise(Unique_Ratings = n_distinct(Rating), Count = n()) %>%
  filter(Count > 1, Unique_Ratings > 1)

print(review_variance)
```

A visualization illustrating rating variation for identical review texts
is provided below:

```{r plot-rating-variation, message=FALSE, warning=FALSE}
review_rating_variation <- newreview %>%
  filter(Review %in% review_variance$Review)

ggplot(review_rating_variation, aes(x = Review, y = as.factor(Rating), color = as.factor(Rating))) +
  geom_jitter(width = 0.3, height = 0.1, size = 2.2, alpha = 0.8) +
  scale_color_brewer(palette = "Dark2") +
  labs(
    title = "Variation in Star Ratings for Identical Reviews",
    subtitle = "Identical reviews submitted with different star ratings",
    x = NULL,
    y = "Star Rating",
    color = "Rating"
  ) +
  theme_minimal(base_size = 13) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, size = 11),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank()
  )
```

------------------------------------------------------------------------

### 4.3 Sentiment and Reply Patterns by Category

This section examines the relationship between review sentiment, reply
behavior, and the classification results. Specifically, we investigate
how sentiment varies across categories and whether certain types of
reviews are more likely to receive a response.

Cross-tabulations were performed to analyze sentiment distributions and
reply behaviors across the *App Experience* and *Other* categories.

```{r sentiment-reply-by-category, message=FALSE, warning=FALSE}
# Cross-tabulate sentiment by predicted label
sentiment_cat_table <- table(newreview$Sentiment, newreview$Predicted_Label)
prop.table(sentiment_cat_table, margin = 2)

# Cross-tabulate reply by sentiment and predicted label
reply_sentiment_table <- table(newreview$Replied, newreview$Sentiment)
# prop.table(reply_sentiment_table, margin = 2)

reply_label_table <- table(newreview$Replied, newreview$Predicted_Label)
# prop.table(reply_label_table, margin = 2)
```

```{r sentiment-category-viz, message=FALSE, warning=FALSE}
# Plot 4: Sentiment distribution by review category
p4 <- newreview %>%
  count(Sentiment, Predicted_Label) %>%
  group_by(Predicted_Label) %>%
  mutate(prop = n / sum(n)) %>%
  ggplot(aes(x = Predicted_Label, y = prop, fill = Sentiment)) +
  geom_col(position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  labs(title = "Sentiment by Review Category", x = "Predicted Label", y = NULL) +
  scale_fill_brewer(palette = "Set2") +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(size = 12))

# Plot 5: Reply rate by sentiment (zoomed and labeled)
p5 <- newreview %>%
  count(Replied, Sentiment) %>%
  group_by(Sentiment) %>%
  mutate(prop = n / sum(n)) %>%
  ggplot(aes(x = Sentiment, y = prop, fill = factor(Replied))) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6) +
  geom_text(aes(label = scales::percent(prop, accuracy = 0.1)), 
            position = position_dodge(width = 0.7), 
            vjust = -0.3, size = 3) +
  labs(title = "Reply Rate by Sentiment (Zoomed)", x = "Sentiment", y = NULL, fill = "Reply") +
  scale_fill_brewer(palette = "Set2") +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(size = 12)) +
  coord_cartesian(ylim = c(0, 0.07))

# Plot 6: Reply rate by predicted label (zoomed and labeled)
p6 <- newreview %>%
  count(Replied, Predicted_Label) %>%
  group_by(Predicted_Label) %>%
  mutate(prop = n / sum(n)) %>%
  ggplot(aes(x = Predicted_Label, y = prop, fill = factor(Replied))) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6) +
  geom_text(aes(label = scales::percent(prop, accuracy = 0.1)), 
            position = position_dodge(width = 0.7), 
            vjust = -0.3, size = 3) +
  labs(title = "Reply Rate by Review Category (Zoomed)", x = "Predicted Label", y = NULL, fill = "Reply") +
  scale_fill_brewer(palette = "Set2") +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(size = 12)) +
  coord_cartesian(ylim = c(0, 0.07))

# Combine vertically
p4 / p5 / p6 + plot_layout(ncol = 1)
```

Key observations include:

-   Among reviews classified as *App Experience*, over **50%** expressed
    **Negative** sentiment, suggesting users frequently raise functional
    frustrations.
-   By contrast, reviews in the *Other* category were **more likely to
    be Positive**, reflecting music enjoyment or general appreciation.
-   Although **only 0.35%** of reviews were replied to overall,
    **responses were concentrated among App Experience and Negative
    reviews**, indicating Spotify's limited replies prioritize user
    complaints about app functionality.

These patterns suggest that Spotify's limited replies are primarily
directed at addressing functionality-related complaints.

------------------------------------------------------------------------

### 4.4 Topic Modeling Within App Experience

To further explore user feedback, I applied Latent Dirichlet Allocation
(LDA) to the subset of reviews classified as *App Experience* by the
TF-IDF Lasso classifier. This helps identify major sub-themes within
app-related reviews.

#### 4.4.1 LDA Modeling

An LDA model with **K = 6** topics was fitted to the preprocessed
document-feature matrix. The number of topics was selected based on the
interpretability and coherence of the resulting themes.

Each review was assigned a dominant topic based on the highest posterior
probability.

```{r lda-app-dfm, eval=FALSE}
# Subset App Experience reviews
app_reviews <- newreview %>% 
  filter(Predicted_Label == "App Experience")

# Create DFM
app_dfm <- tokens(app_reviews$Review,
                  remove_punct = TRUE,
                  remove_numbers = TRUE,
                  remove_symbols = TRUE) %>%
  dfm() %>%
  dfm_remove(stopwords("en")) %>%
  dfm_trim(min_docfreq = 5, docfreq_type = "count")

empty_rows <- which(rowSums(app_dfm) == 0)
length(empty_rows) 

# Set number of topics
K <- 6

# Run LDA model
set.seed(123)
lda_app <- LDA(app_dfm, 
               k = K, 
               method = "Gibbs", 
               control = list(seed = 123, burnin = 1000, iter = 2000))

# Save model and related outputs
saveRDS(lda_app, "model/lda_model_app_experience.rds")
beta_lda <- tidy(lda_app, matrix = "beta")
write.csv(beta_lda, "data/lda_beta_terms.csv", row.names = FALSE)
app_reviews$Topic <- get_topics(lda_app, 1)
write.csv(app_reviews, "data/app_reviews_with_topic.csv", row.names = FALSE)
```

The distribution of reviews across the six topics was checked to ensure
balanced coverage, with each topic capturing a meaningful proportion of
documents.

```{r lda-assign-topics, message=FALSE, warning=FALSE}
# Load saved results
lda_app <- readRDS("model/lda_model_app_experience.rds")
beta_lda <- read.csv("data/lda_beta_terms.csv")
app_reviews <- read.csv("data/app_reviews_with_topic.csv")

# Check how many documents are in each topic
table(app_reviews$Topic)
```

------------------------------------------------------------------------

#### 4.4.2 Topic Interpretation

Top terms for each topic were extracted and visualized.

```{r lda-visualize-top-terms, message=FALSE, warning=FALSE}
# Get top 10 terms per topic
beta_lda <- beta_lda %>% mutate(topic = as.factor(topic))
top_beta_terms <- beta_lda %>%
  group_by(topic) %>%
  slice_max(order_by = beta, n = 10) %>%
  ungroup()

# Plot
top_beta_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(x = beta, y = term, fill = topic)) +
  geom_col(show.legend = FALSE, width = 0.8) +
  facet_wrap(~ topic, scales = "free", ncol = 3) +
  scale_y_reordered() +
  scale_fill_brewer(palette = "Set2") + 
  labs(
    title = "Top 10 Terms per Topic",
    subtitle = "LDA topic modeling on App Experience reviews",
    x = "Beta (Topic-Term Probability)",
    y = NULL
  ) +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 11),
    plot.title = element_text(face = "bold", hjust = 0.5, size = 14),
    plot.subtitle = element_text(hjust = 0.5, size = 11),
    axis.text.y = element_text(size = 10),
    axis.text.x = element_text(size = 10)
  )
```

```{r lda-print-top-terms, message=FALSE, warning=FALSE}
print(top_beta_terms)
# write.csv(top_beta_terms, "data/lda_topic_keywords_top.csv", row.names = FALSE)
```

The dominant topic for each review was assigned based on the maximum posterior probability.

```{r lda-topic-interpretation, message=FALSE, warning=FALSE}
# Extract document-topic probabilities (gamma matrix)
doc_topic_matrix <- tidy(lda_app, matrix = "gamma")

# Rank topics by gamma
doc_topic_ranked <- doc_topic_matrix %>%
  group_by(document) %>%
  arrange(document, desc(gamma)) %>%
  mutate(topic_rank = row_number())

# Top-ranked topic per document
doc_labels <- doc_topic_ranked %>%
  filter(topic_rank == 1) %>%
  select(document, topic, gamma)
head(doc_labels, 10)
```

The six topics identified are:

| Topic                           | Interpretation                                               |
|:---------------------|:------------------------------------------------|
| **Technical Fixes**             | Bugs, app malfunctions, connection issues.                   |
| **Account & Subscription**      | Issues with login, billing, and premium access.              |
| **General UX Feedback**         | Vague usability comments, minor frustrations.                |
| **Playback Issues**             | Playback interruptions, particularly post-updates.           |
| **Music and Playlist Features** | Complaints or praises about playlists and song organization. |
| **Positive Experience**         | Expressions of user satisfaction and loyalty.                |

These categories provide valuable subthemes for understanding the
broader *App Experience* classification. No additional topics (e.g., K =
8 or K = 10) were deemed necessary as this configuration was already
coherent.

These topic labels were subsequently merged back into the full dataset.

```{r lda-topic-labels, message=FALSE, warning=FALSE}
topic_labels <- c(
  "topic_1" = "Technical Fixes",
  "topic_2" = "Account & Subscription",
  "topic_3" = "General UX Feedback",
  "topic_4" = "Playback Issues",
  "topic_5" = "Music and Playlist Features",
  "topic_6" = "Positive Experience"
)

app_reviews$TopicLabel <- paste0("topic_", app_reviews$Topic)
app_reviews$PredictedLabel_LDA <- topic_labels[app_reviews$TopicLabel]
head(app_reviews[, c("Topic", "TopicLabel", "PredictedLabel_LDA")])
```

Reviews not classified as *App Experience* were assigned the label *Other*.

```{r lda-merge-back, message=FALSE, warning=FALSE}
# Merge back with full dataset
newreview$PredictedLabel_LDA <- NA

# Fill in topic labels only for App Experience rows
newreview$PredictedLabel_LDA[newreview$Predicted_Label == "App Experience"] <- app_reviews$PredictedLabel_LDA

# Replace NA with "Other" for non-App Experience
newreview$PredictedLabel_LDA[is.na(newreview$PredictedLabel_LDA)] <- "Other"

# Check label distribution
table(newreview$PredictedLabel_LDA)

# write.csv(newreview, "data/newreview_with_lda_labels.csv", row.names = FALSE)

```

Topic interpretations further confirmed user concerns and praises:

- **Technical Fixes** and **Playback Issues** were primary sources of dissatisfaction.
- **Account & Subscription** issues underscore the importance of seamless service access to maintaining customer loyalty.

```{r wordcloud, message=FALSE, warning=FALSE}
# Get top 50 terms for each topic
par(mfrow = c(2, 3))  # Arrange in a 2x3 grid

top_terms_for_cloud <- beta_lda %>%
  group_by(topic) %>%
  slice_max(order_by = beta, n = 50) %>%
  ungroup()

# Create a lookup for topic labels
topic_label_lookup <- c(
  "1" = "Technical Fixes",
  "2" = "Account & Subscription",
  "3" = "General UX Feedback",
  "4" = "Playback Issues",
  "5" = "Music and Playlist Features",
  "6" = "Positive Experience"
)

# Generate a word cloud per topic with title
for (i in 1:6) {
  topic_data <- top_terms_for_cloud %>% filter(topic == i)
  wordcloud(
    words = topic_data$term,
    freq = topic_data$beta,
    max.words = 50,
    scale = c(3, 0.5),
    colors = brewer.pal(8, "Dark2"),
    random.order = FALSE
  )
  title(main = paste("Topic", i, ":", topic_label_lookup[as.character(i)]))
}
par(mfrow = c(1, 1))  

```

**Topic Interpretations by Word Cloud:**

-   **Topic 1 -- Technical Fixes:** This topic captures reviews
    highlighting technical breakdowns, where users repeatedly mention
    bugs, connection issues, and general malfunctioning. Keywords like
    *fix*, *offline*, *phone*, and *problem* suggest users are facing
    disruptions that prevent basic usage of the app. These reviews tend
    to be urgent, and reflect a desire for immediate resolution. In a
    dataset of over 60,000 reviews, these issues represent one of the
    most common causes for dissatisfaction and tend to be rated poorly.

-   **Topic 2 -- Account & Subscription:** Many users encounter problems
    related to logging in, renewing subscriptions, or accessing
    *premium* features after payment. With terms like *account*, *used*,
    *spotify*, and *premium*, this topic reflects frustration with
    service access or billing irregularities. This issue is particularly
    important given Spotify's business model depends on seamless
    conversion to paid accounts.

-   **Topic 3 -- General UX Feedback:** This topic is marked by
    subjective and general user impressions. Words like *can*, *like*,
    *just*, and *new* imply vague or mixed experiences about the layout,
    buttons, or app responsiveness. The reviews are often neutral in
    sentiment and reflect small annoyances or subtle praises. As a
    middle-ground topic, it highlights areas where UX improvement might
    enhance overall satisfaction.

-   **Topic 4 -- Playback Issues:** Here, users complain about
    interruptions in playback functionality, especially after software
    *updates*. Commonly used terms like *pause*, *playing*, and *stops*
    suggest broken streaming flow. These reviews often report a
    once-functional feature that suddenly fails, making them especially
    frustrating for regular users who rely on the app daily.

-   **Topic 5 -- Music and Playlist Features:** This is the most
    content-focused topic, showing user interaction with the core
    musical experience. Keywords like *songs*, *playlist*, and *listen*
    indicate that users care deeply about how music is organized and
    played. Frustrations arise when shuffle doesn't work or playlists
    behave unexpectedly, but the tone is often less aggressive than
    technical complaints.

-   **Topic 6 -- Positive Experience:** These reviews express gratitude
    and overall delight with Spotify. Words like *music*, *good*,
    *great*, and *love* dominate, showcasing strong user loyalty and
    satisfaction. These reviews frequently highlight the breadth of
    content, smooth interface, or high-quality streaming, and are
    overwhelmingly rated 4 or 5 stars. From a platform perspective, they
    signal what's working well.

------------------------------------------------------------------------

## 5. Platform Reply Analysis

### 5.1 Overview

Spotify replies to only a small portion of user reviews (\~215 out of
over 61,000). To evaluate reply behavior, the dataset ("newreview") is
divided into two groups:

-   Reviews that received an official reply (Replied = 1)
-   Reviews that did not receive a reply (Replied = 0)

------------------------------------------------------------------------

### 5.2 Emotion Scoring Using NRC Lexicon

```{r nrc-emotion-scores, message=FALSE, warning=FALSE}
# Load NRC lexicon
data("get_sentiments")
nrc <- get_sentiments("nrc")

newreview <- newreview %>% 
  mutate(ID = row_number())

# Tokenize reviews
review_tokens <- newreview %>%
  select(ID, Review) %>%
  unnest_tokens(word, Review) %>%
  inner_join(nrc, by = "word")

# Count number of emotion words per review (e.g., anger)
emotion_scores <- review_tokens %>%
  group_by(ID, sentiment) %>%
  summarise(score = n(), .groups = "drop") %>%
  pivot_wider(names_from = sentiment, values_from = score, values_fill = 0)

# Join scores back to main dataset
newreview <- left_join(newreview, emotion_scores, by = "ID")

# Replace NA with 0 for all NRC emotions
emotion_cols <- setdiff(colnames(emotion_scores), "ID")
newreview[emotion_cols] <- lapply(newreview[emotion_cols], function(x) ifelse(is.na(x), 0, x))

# Preview emotion score distribution
summary(newreview$anger)
summary(newreview$joy)
```

------------------------------------------------------------------------

### 5.3 Compare Emotions: Replied vs. Not Replied

```{r nrc-compare-emotions, message=FALSE, warning=FALSE}
# Compare average anger and other emotions between replied vs unreplied reviews
emotion_summary <- newreview %>%
  group_by(Replied) %>%
  summarise(across(all_of(emotion_cols), mean))
```

Emotions for each sub-topics show similar distributions except for the positive feedback.


```{r nrc-compare-emotions-plot, message=FALSE, warning=FALSE}
# Prepare long-format data for plotting
emotion_plot_data <- newreview %>%
  group_by(Replied) %>%
  summarise(across(all_of(emotion_cols), mean)) %>%
  pivot_longer(cols = -Replied, names_to = "Emotion", values_to = "MeanScore") %>%
  mutate(Emotion = str_to_title(Emotion))  # Capitalize for better x-axis labels

# Plot: Emotion levels by reply status
ggplot(emotion_plot_data, aes(x = Emotion, y = MeanScore, fill = factor(Replied))) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6) +
  scale_fill_manual(values = c("#cccccc", "#66c2a5"), labels = c("Not Replied", "Replied")) +
  labs(
    title = "Average Emotion Scores by Reply Status",
    x = "Emotion",
    y = "Average Score",
    fill = "Reply Status"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 30, hjust = 1),
    plot.title = element_text(face = "bold", hjust = 0.5)
  )
```

Different topics seem to share similar distributions of emotion score, except for the **Positive Experience** one.

```{r nrc-compare-plot, message=FALSE, warning=FALSE}
# Prepare long-format data by LDA Topic
emotion_topic_data <- newreview %>%
  group_by(PredictedLabel_LDA) %>%
  summarise(across(all_of(emotion_cols), mean)) %>%
  pivot_longer(cols = -PredictedLabel_LDA, names_to = "Emotion", values_to = "MeanScore") %>%
  mutate(
    Emotion = str_to_title(Emotion),
    PredictedLabel_LDA = str_replace_all(PredictedLabel_LDA, "_", " ")
  )

# Fix visualization: each facet is a topic, X axis is emotion
ggplot(emotion_topic_data, aes(x = Emotion, y = MeanScore, fill = PredictedLabel_LDA)) +
  geom_col(position = position_dodge(width = 0.8), width = 0.6) +
  facet_wrap(~ PredictedLabel_LDA, scales = "free_y", ncol = 2) +
  scale_fill_brewer(palette = "Set3") +
  labs(
    title = "Emotion Scores Across Topics",
    x = "Emotion",
    y = "Average Score",
    fill = "Topic"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(face = "bold", size = 11),
    axis.text.x = element_text(angle = 30, hjust = 1),
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

# Heatmap style: Topic vs Emotion
ggplot(emotion_topic_data, aes(x = Emotion, y = fct_rev(PredictedLabel_LDA), fill = MeanScore)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "#f0f9e8", high = "#08589e") +
  labs(
    title = "Emotion Intensity by Topic",
    x = "Emotion",
    y = "Topic",
    fill = "Avg. Score"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 30, hjust = 1),
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

```


------------------------------------------------------------------------

### 5.4 Logistic Regression: Predicting Replies

This section explores Spotify's reply logic. The model includes multiple
emotional scores from the NRC lexicon, review length, competitor
mentions, and topic labels.

By using the NRC lexicon, we evaluate whether emotional tone correlates
with reply likelihood. Logistic regression results further test if
variables like review length and competitor mentions influence platform
response behavior.

The model is specified as:

$$
\begin{aligned}
\text{logit}(\Pr(\text{Replied}_i = 1)) =&\ \beta_0 + \beta_1 \cdot \text{anticipation}_i + \beta_2 \cdot \text{anger}_i + \beta_3 \cdot \text{disgust}_i + \beta_4 \cdot \text{fear}_i \\
&+ \beta_5 \cdot \text{joy}_i + \beta_6 \cdot \text{sadness}_i + \beta_7 \cdot \text{surprise}_i + \beta_8 \cdot \text{trust}_i \\
&+ \beta_9 \cdot \text{negative}_i + \beta_{10} \cdot \text{positive}_i + \beta_{11} \cdot \text{word\_count}_i \\
&+ \beta_{12} \cdot \text{competitor\_mention}_i + \beta_{13} \cdot \text{PredictedLabel\_LDA}_i + \varepsilon_i
\end{aligned}
$$

```{r logistic-reply-model prepare, message=FALSE, warning=FALSE}
# Add helper features
newreview$word_count <- str_count(newreview$Review, '\\w+')

# Expand list of competitor platforms
competitor_pattern <- "apple music|youtube music|amazon music|tidal|pandora|soundcloud|deezer|qobuz|napster|audiomack|anghami|gaana|jiosaavn|wynk|boomplay|vk music|yandex music|melon|kkbox|netease|kugou|xiami|qq music|pandora|deezer"

newreview$competitor_mention <- ifelse(str_detect(tolower(newreview$Review), competitor_pattern), 1, 0)

# Count number and proportion of reviews mentioning competitors
# table(newreview$competitor_mention)
#prop.table(table(newreview$competitor_mention))
```

**Competitor Analysis**

- Users most frequently mention Pandora, YouTube Music, and Apple Music when discussing alternatives.

```{r competitor, message=FALSE, warning=FALSE}
competitors <- c("apple music", "youtube music", "amazon music", "tidal", "pandora", "soundcloud", "deezer",
                 "qobuz", "napster", "audiomack", "anghami", "gaana", "jiosaavn", "wynk", "boomplay",
                 "vk music", "yandex music", "melon", "kkbox", "netease", "kugou", "xiami", "qq music")

competitor_counts <- sapply(competitors, function(comp) {
  sum(str_detect(tolower(newreview$Review), fixed(comp)))
})

competitor_counts_df <- tibble(
  Competitor = names(competitor_counts),
  Mentions = as.integer(competitor_counts)
) %>%
  arrange(desc(Mentions))

ggplot(competitor_counts_df, aes(x = reorder(Competitor, Mentions), y = Mentions)) +
  geom_col(fill = "#63c2a3") +
  coord_flip() +
  labs(
    title = "Mentions of Competitors in Spotify Reviews",
    x = "Competitor",
    y = "Number of Mentions"
  ) +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold", hjust = 0.5))

# Top 5
top_competitors <- competitor_counts_df %>%
  slice_max(order_by = Mentions, n = 5) %>%
  pull(Competitor)

# only Top 5 review
top_comp_reviews <- newreview %>%
  filter(competitor_mention == 1)  # 只要有mention competitor

comp_emotion_list_top <- lapply(top_competitors, function(comp) {
  top_comp_reviews %>%
    filter(str_detect(tolower(Review), fixed(comp))) %>%
    summarise(across(all_of(emotion_cols), mean, na.rm = TRUE)) %>%
    mutate(Competitor = comp)
})

comp_emotion_top_df <- bind_rows(comp_emotion_list_top)

comp_emotion_top_long <- comp_emotion_top_df %>%
  pivot_longer(cols = -Competitor, names_to = "Emotion", values_to = "AvgScore") %>%
  mutate(Emotion = str_to_title(Emotion))

ggplot(comp_emotion_top_long, aes(x = Emotion, y = AvgScore, fill = Competitor)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6) +
  labs(
    title = "Emotion Scores for Top Competitors",
    x = "Emotion",
    y = "Average Score",
    fill = "Competitor"
  ) +
  scale_fill_brewer(palette = "Set2") +
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5),
    axis.text.x = element_text(angle = 30, hjust = 1)
  )

# Heatmap: Emotion scores for Top 5 Competitors
ggplot(comp_emotion_top_long, aes(x = Emotion, y = reorder(Competitor, -AvgScore), fill = AvgScore)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "#f7fcf0", high = "#006d2c") +  # 柔和绿到深绿
  labs(
    title = "Emotion Intensity for Top Competitors",
    x = "Emotion",
    y = "Competitor",
    fill = "Avg Score"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.text.x = element_text(angle = 30, hjust = 1),
    plot.title = element_text(face = "bold", hjust = 0.5),
    axis.text.y = element_text(size = 10)
  )

```

This bar chart illustrates the average emotion scores for Spotify reviews that mention each of the top five competing platforms. The emotional responses reflect both positive comparisons and points of dissatisfaction, helping Spotify understand user sentiment toward alternatives.

```{r competitor sentiment, message=FALSE, warning=FALSE}
comp_sentiment_list_top <- lapply(top_competitors, function(comp) {
  top_comp_reviews %>%
    filter(str_detect(tolower(Review), fixed(comp))) %>%
    count(Sentiment) %>%
    mutate(Competitor = comp,
           Proportion = n / sum(n))
})

comp_sentiment_df <- bind_rows(comp_sentiment_list_top)


ggplot(comp_sentiment_df, aes(x = Competitor, y = Proportion, fill = Sentiment)) +
  geom_col(position = "fill") +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_brewer(palette = "Set2") +
  labs(
    title = "Sentiment Distribution for Reviews Mentioning Top Competitors",
    x = "Competitor",
    y = "Share of Sentiment",
    fill = "Sentiment"
  ) +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold", hjust = 0.5))
```

While reviews mentioning **Apple Music**, **YouTube Music**, and **Amazon Music** exhibit the highest average scores for *joy* and *positive* emotions, a closer look at sentiment classification reveals a more clear picture:

- **SoundCloud** is most frequently mentioned in *negative* reviews, suggesting that users reference it while expressing dissatisfaction with Spotify or making unfavorable comparisons.
- **YouTube Music** and **Amazon Music** are also frequently cited in *negative* reviews, indicating these competitors are often brought up in complaints or frustrations.
- In contrast, **Apple Music** and **Pandora** are more likely to be mentioned in *positive* or *neutral* reviews, reinforcing their favorable perception among Spotify users.

This contrast between emotional tone and sentiment classification suggests that **positive emotions in competitor mentions do not always reflect positive evaluations of Spotify**. Instead, they may highlight the perceived strengths of rival platforms.

For Spotify, this indicates the need to monitor not only *how often* competitors are mentioned, but also *why*—and in what emotional and evaluative context.

**Descriptive overview for regression**

```{r plot regression variable, message=FALSE, warning=FALSE}
# Plot 7: Word Count Histogram
p7 <- ggplot(newreview, aes(x = word_count)) +
  geom_histogram(bins = 40, fill = "#66c2a5") +
  labs(title = "Review Word Counts Distribution",
       x = "Word Count", y = "Count") +
  theme_minimal(base_size = 11)

# Plot 8: Competitor Mention Bar Plot with % label
competitor_dist <- newreview %>%
  count(competitor_mention) %>%
  mutate(share = round(100 * n / sum(n), 1))

p8 <- ggplot(competitor_dist, aes(x = factor(competitor_mention), y = n, fill = factor(competitor_mention))) +
  geom_col(show.legend = FALSE, width = 0.5) +
  geom_text(aes(label = paste0(share, "%")), vjust = -0.5, size = 4.2) +
  scale_x_discrete(labels = c("0" = "No Competitor", "1" = "Mentions Competitor")) +
  scale_fill_manual(values = c("#fc8d62", "#e34a33")) +
  labs(title = "Competitor Mentions",
       x = "Mentioned", y = "Number of Reviews") +
  ylim(0, max(competitor_dist$n) * 1.1) +
  theme_minimal(base_size = 11)

# Plot 9: LDA Topics Distribution (flipped)
p9 <- newreview %>%
  count(PredictedLabel_LDA) %>%
  ggplot(aes(x = reorder(PredictedLabel_LDA, n), y = n, fill = PredictedLabel_LDA)) +
  geom_col(show.legend = FALSE) +
  labs(title = "Distribution of LDA Topics", x = "Topic Label", y = "Count") +
  scale_fill_brewer(palette = "Set2") +
  coord_flip() +
  theme_minimal()

# Layout
(p7 | p8) / p9
```

```{r logistic-reply-model, message=FALSE, warning=FALSE}
# Logistic regression model using multiple NRC emotions and LDA topic
reply_model <- glm(Replied ~ anticipation + anger + disgust + fear + joy +
                   sadness + surprise + trust + negative + positive +
                   word_count + competitor_mention + PredictedLabel_LDA,
                   data = newreview, family = binomial)


summary(reply_model)

# Compute McFadden's pseudo R-squared
pR2(reply_model)

# Confirm number of observations used
nobs(reply_model)

modelsummary(reply_model, output = "figures/regression_results_table.html")
```

**Key Findings**

-   **Joy** is *negatively associated* with receiving a reply (*p* =
    0.047), suggesting that more cheerful reviews are less likely to get
    a response.

-   **Disgust**, **Positive Sentiment**, and **Trust** are statistically
    significant:

    -   **Disgust** (*p* \< 0.001) and **Positive** (*p* = 0.016) are
        *positively* associated with replies.
    -   **Trust** (*p* = 0.031) is *negatively* associated, indicating
        that trusting language may reduce the likelihood of a response.

-   **Anger**, **Sadness**, **Fear**, and **Surprise** are *not*
    significant predictors.

-   **Word Count** is a strong predictor (*p* \< 0.001): longer reviews
    are more likely to receive a reply.

-   **LDA Topics** matter:

    -   Reviews categorized under **Music and Playlist Features**,
        **Positive Experience**, and **Other** are significantly *less
        likely* to receive a reply compared to the reference category,
        **Account & Subscription**.

-   **Competitor Mention** has no significant effect on reply
    likelihood.

**Model Fit**

-   **McFadden's R² = 0.044**, indicating a modest improvement over the
    null model. While low, this is expected given the rarity of replies
    (\<1%).
-   **Observations**: The model used 60,915 reviews.

**Conclusion**

Spotify appears more responsive to longer reviews with moderate
emotion---especially those expressing dissatisfaction through *disgust*
rather than direct *anger*. While joyful and trusting language reduces
the chance of receiving a reply, technical or account-related
frustrations are more likely to attract attention. Reviews focused on
music features or general positivity tend to be deprioritized in
platform engagement.

### 5.5 Logistic Regression with SMOTE Adjustment

To address class imbalance in the original logistic regression model—where only 3.5% of reviews received replies—I implemented SMOTE to synthetically rebalance the dataset. The adjusted model was trained on the oversampled data and presented alongside the original model.

Key comparisons indicate whether predictors retain statistical significance under balanced conditions, and whether coefficients shift notably due to oversampling. While interpretability may decrease slightly due to synthetic data, the results help validate the robustness of key findings regarding emotional tone and topic labels.

A side-by-side comparison of the original and SMOTE-adjusted model is included.

- SMOTE creates synthetic examples for the minority class (Replied = 1) by interpolating between existing cases.
- It helps the model learn from a more balanced dataset, reducing bias toward the majority class (Not Replied).
- After SMOTE, the number of observations doubles (~60k → ~120k) due to newly generated synthetic records for Replied cases.


```{r SMOTE, message=FALSE, warning=FALSE}
# Prepare data
newreview_bal <- newreview %>%
  select(Replied, anticipation, anger, disgust, fear, joy, 
         sadness, surprise, trust, negative, positive, 
         word_count, competitor_mention, PredictedLabel_LDA) %>%
  mutate(
    Replied = as.factor(Replied),
    PredictedLabel_LDA = factor(PredictedLabel_LDA)
  )

# Ensure consistent reference level
newreview_bal$PredictedLabel_LDA <- relevel(newreview_bal$PredictedLabel_LDA, ref = "Account & Subscription")

# Apply SMOTE (requires numeric predictors only)
smote_input <- newreview_bal %>%
  mutate(PredictedLabel_LDA = as.numeric(PredictedLabel_LDA))  # temporarily convert to numeric for SMOTE

set.seed(123)
smote_result <- SMOTE(smote_input[, -1], smote_input$Replied, K = 5)
smote_data <- smote_result$data
colnames(smote_data)[ncol(smote_data)] <- "Replied"
smote_data$Replied <- as.factor(smote_data$Replied)

# Reconvert topic label to factor with correct reference (because SMOTE strips factor structure)
# Restore topic label as factor using saved levels
topic_levels <- levels(newreview_bal$PredictedLabel_LDA)
smote_data$PredictedLabel_LDA <- factor(
  topic_levels[smote_data$PredictedLabel_LDA],
  levels = topic_levels
)
smote_data$PredictedLabel_LDA <- relevel(smote_data$PredictedLabel_LDA, ref = "Account & Subscription")


# Fit logistic regression model on SMOTE data
reply_model_smote <- glm(Replied ~ ., data = smote_data, family = binomial)

# Show summary
summary(reply_model_smote)

# Calculate McFadden R²
pR2(reply_model_smote)

# Output side-by-side comparison
modelsummary(
  list("Original Model" = reply_model, "SMOTE Adjusted Model" = reply_model_smote),
  output = "figures/logistic_comparison_original_vs_smote_refset.html"
)


```

After correcting for severe class imbalance using SMOTE, most emotional and topic effects remained stable or became stronger. Notably, complaints about Playback Issues turned from a weak positive to a significant negative predictor of receiving a reply, suggesting that Spotify may systematically deprioritize addressing streaming disruptions. The adjusted model reinforces that account and subscription problems are Spotify's top reply priority, while technical bugs and general app frustrations are less likely to elicit a response, reflecting platform-level engagement strategies.

```{r SMOTE-plot, message=FALSE, warning=FALSE}
results <- tribble(
  ~Variable, ~Category, ~Original, ~SMOTE,
  "(Intercept)", "Intercept", -5.528, 0.011,
  "anticipation", "Emotion", 0.049, 0.142,
  "anger", "Emotion", -0.283, -0.202,
  "disgust", "Emotion", 0.464, 0.371,
  "fear", "Emotion", 0.086, -0.106,
  "joy", "Emotion", -0.240, -0.609,
  "sadness", "Emotion", -0.079, 0.069,
  "surprise", "Emotion", 0.107, 0.070,
  "trust", "Emotion", -0.226, -0.212,
  "negative", "Emotion", -0.017, -0.062,
  "positive", "Emotion", 0.179, 0.160,
  "word_count", "Control", 0.010, 0.023,
  "competitor_mention", "Control", -0.103, -0.746,
  "General UX Feedback", "Topic", 0.076, 0.019,
  "Music and Playlist Features", "Topic", -0.717, -0.395,
  "Other", "Topic", -1.031, -0.934,
  "Playback Issues", "Topic", 0.176, -0.148,
  "Positive Experience", "Topic", -0.915, -0.560,
  "Technical Fixes", "Topic", -0.288, -1.098
)

results_long <- pivot_longer(results, cols = c(Original, SMOTE),
                              names_to = "Model", values_to = "Coefficient")

results_long$Variable <- factor(results_long$Variable, 
                                levels = rev(results$Variable))  # 反向一下让图从上到下符合表格顺序

ggplot(results_long %>% filter(Variable != "(Intercept)"), 
       aes(x = Variable, y = Coefficient, fill = Model)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray40") +
  facet_wrap(~ Category, scales = "fixed", nrow = 1) +
  coord_flip() +
  theme_minimal(base_size = 13) +
  labs(title = "Comparison of Coefficient Estimates",
       x = "Variable",
       y = "Coefficient Estimate") +
  scale_fill_manual(values = c("Original" = "steelblue", "SMOTE" = "darkorange")) +
  theme(legend.position = "top",
        strip.text = element_text(size = 12, face = "bold"))


```


After applying SMOTE, nearly all predictors became statistically significant. This is expected because oversampling balances the dataset and substantially increases statistical power, reducing standard errors and enabling the model to detect even small effects. However, caution is necessary: significance does not always imply a large or meaningful effect size, and the model may risk overfitting due to synthetic sample generation. Future validation on an independent dataset is recommended to confirm the robustness of these findings.

------------------------------------------------------------------------

## 6. Discussion

This study aimed to extract actionable insights from Spotify user reviews by applying text-as-data methods, with a focus on understanding user experiences and evaluating platform reply behavior. The findings offer valuable perspectives for both business strategy and digital platform governance.

### 6.1 User Experience Themes and Sentiment Patterns

Analysis of review text through supervised classification and topic modeling confirmed that the majority of user feedback centers around app functionality, technical performance, and usability, rather than music content itself. Reviews classified under *App Experience* topics were notably more likely to receive negative star ratings, underscoring persistent user frustrations with the app's performance and service quality.

Topic modeling further revealed six major sub-themes within App Experience feedback, including technical issues, playback interruptions, account and subscription problems, and general UX feedback. These themes highlight critical areas where user satisfaction is most vulnerable. Moreover, sentiment analysis indicated that emotional expressions such as *disgust* and *trust*—both closely tied to service expectations—were prevalent among users experiencing dissatisfaction.

These results support the initial hypothesis that user-generated content provides a deeper and more nuanced understanding of customer satisfaction drivers, complementing traditional subscription metrics. For business strategy, targeting technical reliability and service accessibility may be pivotal to enhancing user retention.

### 6.2 Platform Reply Behavior and Transparency Implications

Logistic regression analysis of reply likelihood revealed several important patterns. Longer reviews were significantly more likely to receive a reply, suggesting that greater detail prompts more platform engagement. Emotional tone also mattered: reviews expressing *disgust* or *positive sentiment* were more likely to be replied to, while reviews conveying *joy* or *trust* were less likely to attract a response.

In terms of topical focus, reviews related to *account and subscription issues* were significantly more likely to receive replies compared to other categories such as *music and playlist features* or *positive experiences*. This selective engagement strategy indicates that Spotify prioritizes addressing technical service complaints over general user praise or feature feedback.

These findings align with broader concerns in digital platform governance regarding transparency and fairness. Although the overall reply rate was extremely low (under 1%), the selective nature of replies suggests that certain types of dissatisfaction are more visible to the platform, while positive or non-critical feedback may be systematically deprioritized. This asymmetry highlights the importance of transparent communication policies in maintaining user trust and accountability in digital services.

------------------------------------------------------------------------

## 7. Conclusion

- ✅ Most users complain about **app function**, not music (**RQ1 supported**)
- 📉 Spotify replies mostly to **negative, detailed reviews** (disgust, account issues)
- 💬 **Joyful/trusting reviews** are often ignored—missed opportunity to engage satisfied users
- 🛠️ Reply strategy is **reactive (problem)**, not proactive (praise) (**RQ2 supported**)
- 🔄 SMOTE results confirm key findings are **robust**
- ⚠️ **Competitor mentions** show emotion—signal of potential **churn risk**

Overall, this project demonstrates that text-as-data techniques can meaningfully reveal patterns in user experience and platform behavior. Understanding the emotional and thematic structure of user feedback provides actionable insights for service improvement and offers a lens into the operational transparency of digital platforms like Spotify. These results contribute to both business strategy considerations and emerging discussions about consumer protection and platform accountability in the digital economy.

------------------------------------------------------------------------

## 8. References

-   Looka. (2024). *The Spotify Logo: Embodying the sonic style of a
    streaming pioneer*. Retrieved April 2025, from
    <https://looka.com/blog/spotify-logo/>

-   Statista. (2024). *Number of Spotify premium subscribers worldwide
    from 1st quarter 2015 to 4th quarter of 2024*. Retrieved from
    <https://www.statista.com/statistics/244995/number-of-paying-spotify-subscribers/>

-   Pang, B., & Lee, L. (2008). *Opinion mining and sentiment analysis*.
    Foundations and Trends® in Information Retrieval, 2(1--2), 1--135.
    <https://www.nowpublishers.com/article/Details/INR-011>

-   Liu, B. (2012). *Sentiment analysis and opinion mining*. Springer.
    <https://link.springer.com/book/10.1007/978-3-031-02145-9>

-   Tirunillai, S., & Tellis, G. J. (2012). Does online chatter really
    matter? Dynamics of user-generated content and stock performance.
    *Marketing Science*, 31(2), 198--215.
    [https://www.researchgate.net/publication/228151131](https://www.researchgate.net/publication/228151131_Does_Online_Chatter_Really_Matter_Dynamics_of_User-Generated_Content_and_Stock_Performance)

-   Blei, D. M., Ng, A. Y., & Jordan, M. I. (2003). Latent Dirichlet
    Allocation. *Journal of Machine Learning Research*, 3, 993--1022.
    [https://www.researchgate.net/publication/221620547](https://www.researchgate.net/publication/221620547_Latent_Dirichlet_Allocation)

-   Datta, H., Knox, G., & Bronnenberg, B. J. (2018). Changing their
    tune: How consumers' adoption of online streaming affects music
    consumption and discovery. *Marketing Science*, 37(1), 5--21.
    [https://www.researchgate.net/publication/293753759](https://www.researchgate.net/publication/293753759_Changing_Their_Tune_How_Consumers%27_Adoption_of_Online_Streaming_Affects_Music_Consumption_and_Discovery)

-   Piskorski, M. J., Shin, J., & Smith, H. (2019). Social media and
    customer retention: Implications for the luxury beauty industry.
    *Journal of Business Research*, 95, 211--219.
    [https://www.researchgate.net/publication/275947382](https://www.researchgate.net/publication/275947382_Social_Media_and_Customer_Retention_Implications_for_the_Luxury_Beauty_Industry)
